%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4

%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------

% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}



\cvname{Chris Yeomans} % Your name

\cvdate{26 August 1999} % Date of birth
\cvaddress{chrisj.yeomans@gmail.com} % Short address/location, use \newline if more than 1 line is required
\cvnumberphone{089 409 2738} % Phone number

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	 Education
%----------------------------------------------------------------------------------------

\Education{BSC Computational Thinking 2018 - Current
\newline Maynooth University \newline Graduate 2021 \newline LC Points: 509}
%----------------------------------------------------------------------------------------
%	 SKILLS
%----------------------------------------------------------------------------------------

% Skill bar section, each skill must have a value between 0 an 6 (float)
\skills{Languages: Python3, C++, Ruby, Java, C
\newline  WebDev : HTML, CSS, JS, JQuery, Ruby on Rails, Flask(Python3)
\newline Certifications: MS Office 2010 Master
\newline Other: LaTeX, SQL, Docker, Nginx}



\ExtraCurricular{President MU Computer Science Society - Current \\
 - Organising Talks \\
 - Organising Workshops \\
 - Organising Programming Competitions \\
 - Manage Committee
 - Attending Society Council Meetings \newline \newline
Member of the MSU Constitution and Represantative Review Committee \\
 - Attend Meetings \\
 - Review Student Union Constitution}

%------------------------------------------------

% Skill text section, each skill must have a value between 0 an 6

%----------------------------------------------------------------------------------------

\makeprofile % Print the sidebar

%----------------------------------------------------------------------------------------
%	 PROJECTS
%----------------------------------------------------------------------------------------

\section{Projects}

\begin{twenty} % Environment for a short list with no descriptions
	\twentyitem{}{Github}{}{github.com/ChrisYeomans}
	\twentyitem{}{CS Problem Pages}{}{Made a Ruby on Rails website where competitive programming problems can be made and judged. It uses lrun for sandboxing of programs. Complete with unit and system tests and it runs with docker for easy deployment. Currently live at problems.mucss.ie on the Maynooth University Computer Science Society's Server. Project source on Github.}
	\twentyitem{}{Program Poker Sim}{WIP}{A Ruby program that will be put into a Rail application that simultaneously runs multiple programs in a poker simulation and determines the winner. Project source on Github.}
	\twentyitem{}{The Ground}{WIP}{A program that takes a webpage as an entry point and scrapes as much text from the internet as is specified and then uses natural language processing to get word associations with input phrases or words. Project Source on Github.}
	\twentyitem{}{Discord Bots}{}{Bots made using the discord Python3 api. The first one scrapes a gaming news website and outputs any new stories in text form into a specific channel. The second bot uses a cryptocurrency api to give exchange rates on demand. Project sources on Github.}
	\twentyitem{}{Burrito TSP}{}{A project for the module Algorithms and Data Structures 2(CS211). The aim was to take in a list of addresses and give out an ordering of the list with the least time penalty for delivering the burritos "late", 30 minutes after order time was considered late. Project source on Github.}
	\twentyitem{}{House Price Prediction}{}{A project for the module Introduction to Computational Thinking(CS225). The aim of this project was to take in a large csv of historical house sale prices with location and then predict future house sale prices based soley on location. A sqlite3 database also had to be used. Project source on Github.}
	\twentyitem{}{Turing Machine}{}{A project for the module Introduction to Computational Thinking(CS225). The aim of this project was to make a turing machine of 70 bits with an initial program of 30 bits and pront out the longest possible string of 1010101010... Project source on Github.}
\end{twenty}

%----------------------------------------------------------------------------------------
%	 AWARDS
%----------------------------------------------------------------------------------------

\section{Achievements}

\begin{twenty} % Environment for a short list with no descriptions
	\twentyitem{Apr'19}{Progroramma}{}{3rd place in the Programmorama, run by the Maynooth University Computer Science Society.}
	\twentyitem{Mar'19}{IrlCPC}{}{8th place overall in the Irish Collegiate Programming Competition(IrlCPC).}
	\twentyitem{Dec'18}{Xmas Programoramma}{}{2nd place in the Christmas Programmorama, run by the Maynooth University Computer Science Society.}
	\twentyitem{Oct'18}{MU Lovely}{}{4th place in the MU Lovely Programming Competition run by the Maynooth University Computer Science Society.}
	%\twentyitemshort{<dates>}{<title/description>}
\end{twenty}


%----------------------------------------------------------------------------------------
%	 SECOND PAGE EXAMPLE
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\makeprofile % Print the sidebar

%\section{Other information}

%\subsection{Review}

%Alice approaches Wonderland as an anthropologist, but maintains a strong sense of noblesse oblige that comes with her class status. She has confidence in her social position, education, and the Victorian virtue of good manners. Alice has a feeling of entitlement, particularly when comparing herself to Mabel, whom she declares has a ``poky little house," and no toys. Additionally, she flaunts her limited information base with anyone who will listen and becomes increasingly obsessed with the importance of good manners as she deals with the rude creatures of Wonderland. Alice maintains a superior attitude and behaves with solicitous indulgence toward those she believes are less privileged.

%\section{Other information}

%\subsection{Review}

%Alice approaches Wonderland as an anthropologist, but maintains a strong sense of noblesse oblige that comes with her class status. She has confidence in her social position, education, and the Victorian virtue of good manners. Alice has a feeling of entitlement, particularly when comparing herself to Mabel, whom she declares has a ``poky little house," and no toys. Additionally, she flaunts her limited information base with anyone who will listen and becomes increasingly obsessed with the importance of good manners as she deals with the rude creatures of Wonderland. Alice maintains a superior attitude and behaves with solicitous indulgence toward those she believes are less privileged.

%----------------------------------------------------------------------------------------

\end{document} 